Motion planning for assessing accessibility of protein tunnels

### 2017-09-08 paper.tex
missing images

From motion planning point of view, both types of conformations are useful.
The `longer' conformations can better fit in a narrow passage, while the `packed' conformations can be better rotated at place.
To select the suitable conformations, a simple technique is proposed.  
For each conformation, the geometric center is calculated and the deviation of the distances of the atoms from the center is calculated.
The conformations are sorted according to this deviation and then the desired number of conformations are selected from this sorted list uniformly.

@@

{\def\a{270}
\begin{figure}
\centering
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{cccc}
\includegraphics[width=0.15\textwidth,angle=\a]{fig/m001-oneAtom-cdCount} &
\includegraphics[width=0.15\textwidth,angle=\a]{fig/m001-oneAtom-rrt_path_time} &
\includegraphics[width=0.15\textwidth,angle=\a]{fig/m037t-cdCount} & 
\includegraphics[width=0.15\textwidth,angle=\a]{fig/m037t-rrt_path_time} \\
m01 & m01 & m37 & m37 \\

\end{tabular}
\end{figure}
}

>>>>

From motion planning point of view, both types of conformations are useful.
The `longer' conformations can better fit in a narrow passage, while the `packed' conformations can be better rotated at place 
(Fig.~\ref{fig::m040c}.
To select the suitable conformations, a simple technique is proposed.  
For each conformation, the geometric center is calculated and the deviation of the distances of the atoms from the center is calculated.
The conformations are sorted according to this deviation and then the desired number of conformations are selected from this sorted list uniformly.

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{fig/m040-conformations}
\caption{\label{fig::m040c}
 Examples of `long' conformation (left) and a `packed' one for the ligand M040 (1,5-Dichloropentane).
}
\end{figure}

@@

{\def\a{270}
\begin{figure}
\centering
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{cccc}
\includegraphics[width=0.15\textwidth,angle=\a]{fig/m001-oneAtom-cdCount} &
\includegraphics[width=0.15\textwidth,angle=\a]{fig/m001-oneAtom-rrt_path_time} &
\includegraphics[width=0.15\textwidth,angle=\a]{fig/m037t-cdCount} & 
\includegraphics[width=0.15\textwidth,angle=\a]{fig/m037t-rrt_path_time} \\
\multicolumn{2}{c}{One-atom} &
\multicolumn{2}{c}{m037}  \\
\multicolumn{4}{c}{%
\includegraphics[width=0.15\textwidth,angle=\a]{fig/m040-10-cdCount} 
\includegraphics[width=0.15\textwidth,angle=\a]{fig/m040-10-rrt_path_time} 
\includegraphics[width=0.15\textwidth,angle=\a]{fig/m040-10-trajDistToGoal}} \\
\multicolumn{4}{c}{m040} 
\end{tabular}
\end{figure}
}
